---
title: "BMI 881 Homework 1"
author: "Li Ge"
date: "`r Sys.Date()`"
output: pdf_document
urlcolor: blue
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  fig.align = "center"
)

```

This is the [link](https://kbroman.org/BMI881/homework1.html) to the homework.

## Design Choices

* Apparently, the data can be divided into two parts. One part contains the *year, age_group, income_group*, the other part contains the *mortality_rate, interval_low, interval_high*. I should find a way to arrange these different groups. And I should always present the mortality rate together with its interval. ggplot2's facet_grip and geom_pointrange seem to be the perfect fit for it.

* I was originally planning to design a facet_grid with *income_group v. age_group*, each subplot is the *mortality v. year*. But then I realized it would be difficult to compare the mortality rate between different income groups. So I decided to use color to indicate different income groups. And it was so much better.

* Because the mortality rates are drastically different between *>=75 v. rest*. I made 2 figures. For the first one, I used different y-axis for each subplot, which makes the range more obvious. I log-scaled the y-axis for the second graph for easier comparison across all age groups.

```{r}
library(ggplot2)
# read the data
stroke <- read.csv("https://kbroman.org/BMI881/assets/feigin2014_table1_mortality.csv")

# plot
ggplot(data = stroke, mapping = aes(x = year, y = mortality_rate, color = income_group)) + 
  facet_wrap(. ~ age_group, scale = "free_y") + 
  geom_pointrange(aes(ymin = interval_low, ymax = interval_high), alpha = 0.5) + 
  geom_line()

ggplot(data = stroke, mapping = aes(x = year, y = mortality_rate, color = income_group)) + 
  facet_wrap(. ~ age_group) + 
  scale_y_log10() +
  geom_pointrange(aes(ymin = interval_low, ymax = interval_high), alpha = 0.5) + 
  geom_line()

```

## Conclusions

* *>=75* age group has the highest mortality rate.

* The higher the income, the lower the mortality rate.

* The mortality rate decreased over the years.

## Code

```{r ref.label = knitr::all_labels(), echo = TRUE, eval = FALSE}
# this R markdown chunk generates a code appendix
```